### 2025-09-25 paper/sec/evaluation.tex
Contribs.

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfour}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & 74.7   & 3 & 77.4 & 2 \\
            Data Retrieval & 76.4   & 3 & 77.4 & 2 \\
            Difference     & 80.3   & 3 & 77.4 & 2 \\
            Min/max        & 50.2   & 3 & 77.4 & 2 \\
            Rank           & 44.1   & 3 & 77.4 & 2 \\
            Total          & 33.2   & 3 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & -- & -- & -- & -- \\
            Data Retrieval & -- & -- & -- & -- \\
            Difference     & -- & -- & -- & -- \\
            Min/max        & -- & -- & -- & -- \\
            Rank           & -- & -- & -- & -- \\
            Total          & -- & -- & -- & -- \\
            Overall        & -- & -- & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{\gptfour} and \textbf{\gptfive} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}

>>>>

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 68.2   & 3.2 & 77.4 & 2 \\
            Data Retrieval & 77.3   & 3.7 & 77.4 & 2 \\
            Difference     & 20.0   & 44.7 & 77.4 & 2 \\
            Min/max        & 97.0   & 5.6 & 77.4 & 2 \\
            Rank           & 0.0   & 0.0 & 77.4 & 2 \\
            Sum            & 100   & 0.0 & 77.4 & 2 \\
            Ratio          & 100   & 0.0 & 77.4 & 2 \\
            Agerage        & 100   & 0.0 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 33.3 & 3.1 & -- & -- \\
            Data Retrieval & 62.0 & 1.6 & -- & -- \\
            Difference     & 75.0 & 50.0 & -- & -- \\
            Min/max        & 90.6 & 12.6 & -- & -- \\
            Rank           & 0.0 & 0.0 & -- & -- \\
            Sum            & 100.0 & 0.0 & -- & -- \\
            Ratio          & 100.0 & 0.0 & -- & -- \\
            Average        & 100.0 & 0.0 & -- & -- \\
            Overall        & 57.1 & 0.8 & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{\gptfour} and \textbf{\gptfive} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}
